My title

### 2024-11-04 paper/paper.qmd
finalized model and predicitons

@@

@@

>>>>

trumpdata <- preddata %>%
  filter(state %in% c("Georgia", "Arizona", "Nevada", "Michigan", "North Carolina", "Pennsylvania", "Wisconsin")) %>%
  filter(candidate_name == "Donald Trump") %>%
  mutate(end_date = mdy(end_date)) %>%
  filter(end_date >= as.Date("2024-07-21")) %>%
  mutate(num_trump = round((pct / 100) * sample_size, 0))

combined_data <- harrisdata %>%
  inner_join(trumpdata, by = c("state", "pollster", "sample_size", "end_date")) %>%
  mutate(
    harris_percentage = (num_harris / sample_size) * 100,
    trump_percentage = (num_trump / sample_size) * 100
  )

time_series_data <- combined_data %>%
  select(state, harris_percentage, trump_percentage) %>%
  pivot_longer(cols = c(harris_percentage, trump_percentage),
               names_to = "candidate",
               values_to = "support_percentage") %>%
  mutate(candidate = ifelse(candidate == "harris_percentage", "Harris", "Trump"))

# Plotting the support percentages side-by-side for each state
plot_data <- combined_data %>%
  pivot_longer(cols = c(harris_percentage, trump_percentage),
               names_to = "candidate",
               values_to = "support_percentage") %>%
  mutate(candidate = ifelse(candidate == "harris_percentage", "Harris", "Trump"))

# Plotting the support percentages side-by-side for each state
ggplot(plot_data, aes(x = state, y = support_percentage, fill = candidate)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7)) +
  labs(
    title = "Support Percentages for Harris and Trump by State",
    x = "State",
    y = "Support Percentage"
  ) +
  scale_fill_manual(values = c("Harris" = "blue", "Trump" = "red"), name = "Candidate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

```
```{r}
expected_probs <- posterior_epred(bayesian_model, newdata = harrisdata)

# Calculate the mean predicted probability across all observations (overall predicted support percentage)
overall_predicted_support <- mean(rowMeans(expected_probs)) * 100
overall_predicted_support

@@

```{r}
expected_probs <- posterior_epred(bayesian_model, newdata = harrisdata)

# Calculate the median predicted probability for each observation
median_probs <- apply(expected_probs, 2, median)

# Add median predicted probabilities to `harrisdata`
harrisdata <- harrisdata %>%
  mutate(median_prob = median_probs)

# Calculate the average predicted support by state
predicted_support_table <- harrisdata %>%
  group_by(state) %>%
  summarize(average_predicted_support = mean(median_prob) * 100)

# Print the table
predicted_support_table
```
